\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-04 cfhtlens.tex
plots added to tex

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/ellWnPell1-100.pdf}
\caption{ \label{fig:filters}.  Currently just COSEBIS, will also have $\xi_\pm$ and $M_{\rm ap}^2$.}
\end{center}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/IntegKsip.pdf}\\
\includegraphics[width=0.5\textwidth]{figures/IntegCOSEBIs.pdf}\\
\includegraphics[width=0.5\textwidth]{figures/IntegMap.pdf}
\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ and $M_{\rm ap}$.
All the values are normalized with respect to their maximum value. Two cases are shown for each statistic. 
For COSEBIs this is an angular range indicated in the caption. For aperture mass statistic $\theta_{\rm max}=2\theta$ is shown.
}
\end{center}
\end{figure}
